---
title: "Final_project_explaination_log_normal"
author: "Hayden Joy"
date: "11/19/2019"
output: pdf_document
---

Let's assume that our stock variables are log-normally distributed. This is better than assuming that they are normally distributed because our support is strictly positive.
This is what I did to combine the stock data. This means that the log of X is normally distributed.

Further, we allow for a right skewed distribution which can account for surging stock prices like Amazon ect.

$$X\thicksim\mathcal{LN}$$
$$log(X)\thicksim\mathcal{N}(\mu, \sigma^2)$$
This means that:
$$X=  e^{\mu + \sigma Z}$$
So to get standardized normal random variables we can do the following:

$$(log(X)-\mu)/\sigma=Z$$

```{r}
hi<-c(1,2,3)
sample(hi,5, replace = T)
```


```{r}
stocks<-read.csv("log_adj_amer_combo.csv")
#install.packages("ks")
require("ks")

nroww <- nrow(stocks)

for (col in colnames(stocks)[3:length(colnames(stocks))-1])
{
  stock_spec  <- col
  delt <- rep(NA, nrow(stocks)-1)
  prev <- NA
  dummyx <- 1:(nrow(stocks)-1)
  for (i in 1:nrow(stocks))
  {
    this <- stocks[i, stock_spec]
    if( i > 1)
    {
      delt[i-1] <- this - prev
    }
    prev <- this
  }
  stocks[2:nroww,paste0(col, "_delt")]<- delt
  head(delt)
  plot(delt ~ dummyx)
  lm1 <- lm(delt ~ dummyx)
  booted <- sample(na.omit(delt),nroww,replace = T)
  print(length(na.omit(delt)))
  if((length(booted)-1) == length(na.omit(delt)))
  {
    hist(delt, breaks = 20, col = "blue",main = col,  xlab = "blue is the log-normally adjusted price, red is normal dist")
  }
  else{
    hist(booted, breaks = 20, col = "blue",main = col,  xlab = "blue is the log-normally adjusted price, red is normal dist")
    print("ALT")
  }
  
  dummyx <- seq(-0.6,0.6, 0.01)
 
  y <- rnorm(n = length(delt), mean = 0, sd = sd(booted))#* (sqrt(length(na.omit(delt)))/sqrt(length(delt)))
  library("scales")
  hist(na.omit(y), add = T, col = alpha("red", 0.5))
}

head(stocks)

```
<!---
```{r}
stocks<-read.csv("log_adj_chinese_combo.csv")
#install.packages("ks")
require("ks")

nroww <- nrow(stocks)
rm(seqq)
seqq_base <- 0.4
seqq<- rep(0.6, 5)
print(seqq)

for ( l in 1:length(seqq))
{
  seqq[l] = seqq_base^l
}
seqq <- seqq / sum(seqq)
print(paste("sequqnce: ", seqq))

for (col in colnames(stocks)[3:length(colnames(stocks))-1])
{
  stock_spec  <- col
  delt <- c()
  prev <- c(NA,NA)

  for (i in 1:nrow(stocks))
  {
    this <- stocks[i, stock_spec]
    if( i > 5)
    {
      auto_regg_1 <- this - stocks[i - 1, stock_spec] 
      auto_regg_2 <- (stocks[i -1, stock_spec] - stocks[i - 2, stock_spec])  * seqq[1]
      auto_regg_3 <- (stocks[i -2, stock_spec] - stocks[i - 3, stock_spec])  * seqq[2]
      auto_regg_4 <- (stocks[i -2, stock_spec] - stocks[i - 3, stock_spec]) * seqq[3]
      auto_regg_5 <- (stocks[i -3, stock_spec] - stocks[i - 4, stock_spec]) * seqq[4]
      auto_regg   <- c(auto_regg_1, auto_regg_2, auto_regg_3, auto_regg_4,auto_regg_5 )
      auto_regg   <- na.omit(auto_regg)
      #auto_regg  <- auto_regg[auto_regg <= 1]
      delt <- c(delt, auto_regg[1] + auto_regg[2] + auto_regg[3] + auto_regg[4] + auto_regg[5])
    }
    prev[2] <- prev[1]
    prev[1] <- this
  }
  

  stocks[(nroww - length(delt)+1):nroww,paste0(col, "_delt")]<- delt
  dummyx <- 1:(length(delt))
  head(delt)
  plot(delt ~ dummyx)
  lm1 <- lm(delt ~ dummyx)
  booted <- sample(na.omit(delt),nroww,replace = T)
  print(length(na.omit(delt)))
  
  
  
  booted <- sample(na.omit(delt),nroww,replace = T)
  #print(length(na.omit(delt)))
  if((length(booted)-1) == length(na.omit(delt)))
  {
    hist(delt, breaks = 20, col = "blue",main = col,  xlab = "blue is the log-normally adjusted price, red is normal dist")
  }
  else{
    hist(booted, breaks = 20, col = "blue",main = col,  xlab = "blue is the log-normally adjusted price, red is normal dist")
    print("ALT")
  }
  
  dummyx <- seq(-0.6,0.6, 0.01)
 
  y <- rnorm(n = length(delt), mean = 0, sd = sd(booted))#* (sqrt(length(na.omit(delt)))/sqrt(length(delt)))
  library("scales")
  hist(na.omit(y), add = T, col = alpha("red", 0.5))
}

head(stocks)

```
--->
